A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-02-08 doc/draft-01-stokes/01intro.tex
clean up stokes manuscript, update matlab routines

Consider the pure bending of an isotropic and homogeneous thin clamped
plate. 
Let $\Omega$ denote the midline of the plate, $\Gamma$ denote the 
boundary of $\Omega$ and $w$ denote the vertical displacement.
The buckling problem consists of finding 
values $k^{2}$ such that the boundary value problem

\begin{align}
\Delta (\Delta + k^2) w &= 0 \quad \textrm{in} \quad \Omega \label{eq:buck1} \; , \\
w &= 0 \quad \textrm{on} \quad \Gamma \label{eq:buck2} \; ,\\
\dwdn &=0 \quad \textrm{on} \quad \Gamma \label{eq:buck3} 
\end{align}
has a non-trivial solution. In a slight abuse of notation,
these values and the corresponding solutions are often
referred to as ``eigenvalues'' and ``eigenfunctions'',
respectively. 
It is well known that the buckling problem has a
countable collection of such values
$0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
counting multiplicites.

\begin{remark}
  When $k = i\alpha$, the differential equation
  \cref{eq:buck1} is known as the modified biharmonic
  equation. As there appears to be no preferred
  name for the equation with real-valued $k$,
  we will refer to \cref{eq:buck1} as the
  Helmholtz-biharmonic equation.
\end{remark}

The eigenvalues (and eigenfunctions)
of the boundary value problem \cref{eq:buck1,eq:buck2,eq:buck3}
describe the critical buckling load (and deflection)
of a thin plate under
a compressive force applied along the edge. While the
isotropy and homogeneity assumptions are restrictive,
the equations are still of interest in materials design
(CITATIONS). The analytical properties of the eigenvalues and
eigenfunctions are also of interest from a mathematical
perspective, often as they contrast with the eigenvalues
and eigenmodes of an idealized drum (CITATIONS). For instance,
it is well-known that the first eigenfunction of the
drum problem (i.e. the eigenvalue problem of the Laplace
equation with homogeneous Dirichlet boundary conditions)
is either nonpositive or nonnegative on any domain.
In contrast, it is possible for the first buckling
eigenfunction of a convex domain with analytic boundary
to take both positive and negative values \cite{antunes2011buckling}.

Numerical simulations have long played an important
role in the analyses described above and there are a number
of available methods (note that some of the references
included here are written in terms of the related
Stokes eigenvalue problem, which has equivalent
eigenvalues on simply connected domains). We do not
seek to review the literature here but will provide
some context for the present work. Finite element methods
are ubiquitous in mechanical engineering applications
and are flexible with respect to both the governing
equations and the shape of the domain. Such a method
would first obtain a ``weak'' form of the equations
\cref{eq:buck1,eq:buck2,eq:buck3} and then 
approximate the solution space in some
finite dimensional basis, resulting in a discrete model
for the buckling problem.
The eigenvalues $k^2$ are then
approximated by the eigenvalues of the discrete
model \cite{johnson1974beam,rannacher1979nonconforming,
  jia2009approximation,carstensen2014guaranteed}.
Because of the fourth order term in \cref{eq:buck1},
the system matrices resulting from a finite element
discretization can have large condition numbers (growing
like $1/h^4$ where $h$ is the diameter of a typical element
in the discretization) which can cause numerical instability.

Integral equation methods \cite{kress1989linear,
  atkinson2009numerical,kitahara2014boundary} present
a natural alternative to the finite element method
for the buckling problem, because (a) the
integral representation acts as an analytical preconditioner
for the fourth order term and (b) the problem is reduced
to one defined on the boundary of the domain alone,
requiring fewer degrees of freedom to resolve the solution
on a complex domain. In an integral equation method,
the solution $w$ is represented in terms of a sum of
two layer potentials (which a priori satisfy
\cref{eq:buck1}) with unknown densities. Substituting this
representation into the boundary conditions
\cref{eq:buck2,eq:buck3} results in an integral equation
for the unknown densities, which
is in turn discretized using numerical quadrature.
Unlike the original equation \cref{eq:buck1} and the weak
formulation used in a finite element method, the integral
equation for the unknown densities has a nonlinear dependence
on the parameter $k^2$. In an integral equation method, then,
the eigenvalues are found by searching for the values
of $k^2$ where the discrete system for the unknown densities
is no longer invertible.

While integral equation methods for the buckling problem
have been considered previously, the existing formulations
have resulted in first kind integral equations, i.e. equations
in which the operator is compact \cite{kitahara2014boundary,
  antunes2011buckling}. This is unsatisfying from a theoretical
perspective, because such operators are never invertible
(though, they are injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary}) so that the
relation between the non-invertibility of the discrete system
and the eigenvalues is obscured. Further, such representations
create numerical challenges because common measures of the
``non-invertibility'' of a matrix, like the smallest singular
value or the determinant, converge rapidly to zero for all
values of $k^2$ as the boundary is refined. Therefore, the
measure of whether $k^2$ is an approximate eigenvalue is
{\em relative to the current grid} for first kind equations.

Second kind integral equations, i.e. integral equations
of the form $\mathcal{I} + \mathcal{K}$ where $\mathcal{K}$
is compact, have a more satisfying theory
\cite{reed1972methods,kress1989linear},
which translates well to numerical implementation
\cite{atkinson2009numerical,bornemann2010numerical,
  hackbusch2012integral,zhao2015robust}. Two facts are
of particular importance here: with an appropriately
chosen representation, (a) the Fredholm determinant of the
integral equation will be a well-defined analytic function
of $k^2$ with zeros precisely at the eigenvalues and (b) the 
determinant of the matrix resulting from
a Nystr\"{o}m discretization of the integral equation
will converge to the Fredholm determinant of the operator
\cite{bornemann2010numerical}.
In \cite{zhao2015robust}, Zhao and Barnett demonstrated
that the eigenvalues of the drum problem can be
computed with such a framework, resulting in
methods which are spectrally accurate with respect
to both the sampling of the boundary and the sampling
in $k^2$. There are natural extensions of existing second
kind integral
equations for the biharmonic \cite{farkas1989mathematical}
and modified biharmonic \cite{jiang2013second} equations
which would be appropriate for the buckling problem, but
these representations suffer from instability for
high curvature domains, limiting their applicability
\cite{rachh2017integral}.

In this paper, we develop a second kind integral
equation for the buckling problem based on Stokeslet
and stresslet inspired kernels, as was done for the
$k=0$ case in \cite{rachh2017integral}. This allows
for a robust approach to computing the eigenvalues
of the buckling problem, modeled after the approach for
the drum problem in \cite{zhao2015robust}, which we
demonstrate with a number of examples from the
literature.

The rest of this paper is organized as follows ...

>>>>

The planar incompressible Stokes equations describe
creeping flow in two dimensions. Let $\Omega \subset \R^2$
be a domain with $C^2$ boundary. The eigenvalue problem seeks
values $k^2$ such that

\begin{align}
  -\Delta \uu + \nabla p &= k^2 \uu \quad \textrm{in} \quad
  \Omega \label{eq:ostokes} \; , \\
  \nabla \cdot \uu &= 0 \; , \label{eq:ostokescty}
\end{align}
subject to certain boundary conditions, has a non-trivial solution.
Let $\bsigma(\uu,p)$ denote the Cauchy stress tensor
associated with the flow (defined below) and let $\bnu$ denote
the outward normal along the boundary.
In this work, we consider both the Dirichlet boundary condition,
\begin{equation}
  \uu = \bz \quad \textrm{on} \quad \Gamma \label{eq:ostokes_dir} \; ,
\end{equation}
and the Neumann boundary condition,
\begin{equation}
  \bsigma( \uu, p ) \cdot \bnu  = \bz \; . \label{eq:ostokes_neu}
\end{equation}
It is well known that there is a countable collection of such
values $0 < k_{1}^{2} \leq k_{2}^2 \leq \ldots \uparrow \infty$,
counting multiplicites.

\begin{remark}
  When $k = i\alpha$, the differential equation
  \cref{eq:ostokes} is known as the modified Stokes
  equation. As there appears to be no preferred
  name for the equation with real-valued $k$,
  we will refer to \cref{eq:ostokes} as the
  oscillatory Stokes equation.
\end{remark}

### 2019-02-08 doc/draft-01-stokes/02prelim.tex
clean up stokes manuscript, update matlab routines

@@

Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
for sufficiently smooth $f$
\begin{equation}
  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
\end{equation}
We consider here
``free-space'' Green's functions, i.e. fundamental solutions which satisfy
some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
The Green's function of the oscillatory biharmonic equation
\cref{eq:buck1} is given by 
\begin{equation}
  \Gbh(\xx,\yy) = \frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, , 
\end{equation}
where $k$ is the Helmholtz paramater in the oscillatory biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
Note that this is a scaled difference of the Green's function for
Laplace, i.e.

\begin{equation}
  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; ,
\end{equation}
and the Green's function for the Helmholtz equation

\begin{equation}
  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; .
\end{equation}

@@

The Stokes eigenvalue problem (with ``no-slip'' boundary conditions)
seeks values $k^2$ such that the equations
\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= 0 \quad \textrm{in} \quad \Omega
  \; , \label{eq:helmstokes}\\
  \nabla \cdot \uu &= 0 \quad \textrm{in} \quad \Omega
  \; , \label{eq:helmstokescty} \\
  \uu &= 0 \quad \textrm{on} \quad \Gamma \; \label{eq:helmstokesnoslip}
\end{align}
have a non-trivial solution. In the case that $k=i\alpha$ for
some real-valued $\alpha$, the equations \cref{eq:helmstokes,eq:helmstokescty}
are known as the modified Stokes equations and are of particular
interest for their application to numerical simulations of unsteady
flow
\cite{pozrikidis1992boundary,biros2002embedded,jiang2013second}.
In the absence of a preferred name for the case of real-valued $k$,
we will refer to \cref{eq:helmstokes,eq:helmstokescty} as the
oscillatory Stokes equations.

\subsubsection{Stokeslets and stresslets}

@@

 Consider the solution of
\cref{eq:helmstokes,eq:helmstokescty} where a $\delta$-mass
centered at $\yy$ with strength $\ff$
has been added to the right-hand side of \cref{eq:helmstokes}, i.e.

\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
  \label{eq:helmstokes_charge} \\
  \nabla \cdot \uu &= 0 \; .
\end{align}
Recall that

\begin{equation}
 \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; .
\end{equation}
If we substitute this expression into
\eqref{eq:helmstokes_charge} and take the divergence,
we obtain

\begin{equation}
  p = \nabla \Glap(\xx,\yy) \cdot \ff \; .
\end{equation}
We then have, formally,

\begin{align}
  \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
  - \nabla (\nabla \Glap \cdot \ff ) ) \\
  &= \left ( -\Delta + \nabla \otimes \nabla \right )
  \Gbh \ff \; .
\end{align}
The tensor

\begin{equation} \label{eq:stokeslet}
  \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
\end{equation}
is then the equivalent of a Stokeslet
\cite{pozrikidis1992boundary} for the problem
\eqref{eq:helmstokes}.

A related object is the stresslet, which is defined
in terms of the stress tensor of a velocity, pressure
pair induced by a Stokeslet. For these tensors, we find
that it is more convenient to express them in index notation
with the Einstein index summing convention.
Recall that the stress tensor $\bsigma$ is defined as

\begin{equation}
  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
  +\partial_{x_i} u_j \right ) \; ,
\end{equation}
where $\delta_{ij}$ is the standard Kronecker delta notation.
The stresslet $\TT$ is defined to be

\begin{align}
  T_{ijk} &= - \partial_{x_j} \Glap \delta_{ik}
  + \partial_{x_k} \left ( -\Delta \Gbh \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{kj} +
  \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
  \; .
\end{align}
Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} \Glap f_i$ be a
solution of the Stokes equations induced by a Stokeslet.
Then the corresponding stress tensor is given by
$\sigma_{ik} = T_{ijk} f_j$.

@@

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  + \partial_\nu \left ( -\Delta \Gbh \II
  + \nabla \otimes \nabla \Gbh \right)
  + \nabla \otimes \left ( -\Delta \Gbh \bnu
  + \partial_{\nu} \nabla \Gbh \right) \; .
\end{equation}
%\begin{align}
% -\Delta \Gbh \bnu
% + \partial_{\nu} \nabla \Gbh &=
% ( (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_1 \Gbh +
% (\partial_{x_1x_1}\nu_1 + \partial_{x_2x_1} \nu_2 )\Gbh,
% (-\partial_{x_1x_1}-\partial_{x_2x_2}) \nu_2 \Gbh +
% (\partial_{x_1x_2}\nu_1 + \partial_{x_2x_2} \nu_2 )\Gbh) \\
% &= (-\partial_{x_2} \partial_\tau \Gbh,
% \partial_{x_1} \partial_\tau \Gbh)
%\end{align}
%\begin{equation}
%  \begin{pmatrix}
%    -\partial_{x_2x_2} & \partial_{x_1x_2} \\
%    \partial_{x_1x_2} & -\partial_{x_1x_1}
%  \end{pmatrix} = -\nabla^\bot \otimes \nabla^\bot
%\end{equation}
Let $\btau = \bnu^\bot$. Then

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
\end{equation}

\subsubsection{Layer potentials and integral representation}

We now use the Stokeslet and stresslet definitions
of the previous section to define the standard single
and double layer potentials of the Stokes eigenvalue
problem. The single layer potential is defined to
be

\begin{equation}
  \SS \bmu (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy) \; .
\end{equation}
The double layer potential is defined to be

\begin{equation} \label{eq:doublelayer}
  \DD \bmu (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where $\bnu$ denotes the outward unit normal to the boundary.
If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
where $\btau = \bmu^\bot$ is the positively oriented unit
tangent to the curve, then we have

\begin{align} \label{eq:stokesdlkernel}
  \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy) \right )^\intercal
  \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
  \partial_{\nu\tau} \Gbh(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
  & \qquad+
  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
  \Gbh(\xx,\yy) \mu_\tau(\yy) \; .
\end{align}

>>>>

For a given velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
denote the Cauchy stress tensor, i.e.
\begin{equation}
\bsigma(\uu,p) = -p \II + 2 \be(\bu) \, ,
\end{equation}
where $\be(\bu)$ is the strain tensor given by
\begin{equation}
e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
\end{equation}
When it is clear from context, we will drop the dependence of
$\bsigma$ on $\bu$ and $p$.

@@

Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
for sufficiently smooth $f$
\begin{equation}
  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, dy = f(\xx) \; .
  \nonumber
\end{equation}
We consider here
``free-space'' Green's functions, i.e. fundamental solutions which satisfy
some natural growth or decay conditions as $|\xx-\yy| \to \infty$.
The Green's function of the oscillatory biharmonic equation,
\begin{equation}
  \Delta ( \Delta + k^2 ) u = 0 \; , \label{eq:obiharm} \nonumber
\end{equation}
is given by 
\begin{equation}
  \Gbh(\xx,\yy) = \frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, ,
  \label{eq:Gbh}
\end{equation}
where $k$ is the Helmholtz paramater in the oscillatory biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
Note that this is a scaled difference of the Green's function for
Laplace, i.e.

\begin{equation}
  \Glap(\xx,\yy) = \frac{1}{2\pi} \log |\xx-\yy| \; , \nonumber
\end{equation}
and the Green's function for the Helmholtz equation

\begin{equation}
  \Ghelm(\xx,\yy) = -\frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \; . \nonumber
\end{equation}

@@

In the case that $k=i\alpha$ for some real-valued $\alpha$,
the equations \cref{eq:ostokes,eq:ostokescty}
are known as the modified Stokes equations and are of particular
interest for their application to the analysis and numerical
simulation of unsteady flow
\cite{pozrikidis1992boundary,biros2002embedded,
  jiang2013second,ladyzhenskaya1969mathematical}.
The equations are well-studied in that setting and
integral representations which lead to second kind
integral equations have been developed. We review
some of the relevant results here, translating to
the present, oscillatory setting.

\subsubsection{Oscillatory Stokeslets and stresslets}

@@

 Consider the solution of
\cref{eq:ostokes,eq:ostokescty} where a $\delta$-mass
centered at $\yy$ with strength $\ff$
has been added to the right-hand side of \cref{eq:ostokes}, i.e.

\begin{align}
  \nabla p - \Delta \uu - k^2 \uu &= \delta_\yy \ff \; ,
  \label{eq:ostokes_charge}  \\
  \nabla \cdot \uu &= 0 \; . \nonumber
\end{align}
Recall that

\begin{equation}
 \Delta \Glap(\xx,\yy) = \delta_\yy(\xx) \; . \label{eq:lapdelta}
\end{equation}
If we substitute \eqref{eq:lapdelta} into
\eqref{eq:ostokes_charge} and take the divergence,
we obtain

\begin{equation}
  p = \nabla \Glap(\xx,\yy) \cdot \ff \; . \nonumber
\end{equation}
We then have, formally,

\begin{align}
  \uu &= - (\Delta + k^2)^{-1} ( \Delta \Glap \ff
  - \nabla (\nabla \Glap \cdot \ff ) ) \nonumber \\
  &= \left ( -\Delta + \nabla \otimes \nabla \right )
  \Gbh \ff \; . \nonumber
\end{align}
The tensor

\begin{equation} \label{eq:ostokeslet}
  \GG = - \II \Delta \Gbh + \nabla \otimes \nabla \Gbh
\end{equation}
is then the equivalent of a Stokeslet
\cite{pozrikidis1992boundary} for the problem
\eqref{eq:ostokes}.

A related object is the stresslet, which is defined
in terms of the stress tensor of the velocity, pressure
pair induced by a Stokeslet. For these tensors, we find
that it is more convenient to express them in index notation
with the Einstein index summing convention.
Recall that the stress tensor $\bsigma$ is defined as

\begin{equation}
  \sigma_{ij} = -p \delta_{ij} + \left ( \partial_{x_j}u_i
  +\partial_{x_i} u_j \right ) \; , \nonumber
\end{equation}
where $\delta_{ij}$ is the standard Kronecker delta notation.
The stresslet $\TT$ is defined to be

\begin{align}
  T_{ijk} &= - \partial_{x_j} \Glap \delta_{ik}
  + \partial_{x_k} \left ( -\Delta \Gbh \delta_{ij} +
  \partial_{x_i} \left(\partial_{x_j} \Gbh \right) \right)
  \nonumber \\
  & \qquad+ \partial_{x_i} \left ( -\Delta \Gbh \delta_{kj} +
  \partial_{x_k} \left(\partial_{x_j} \Gbh \right) \right)
  \; . \label{eq:ostress} \nonumber
\end{align}
Let $u_i = G_{ij} f_j$ and $p = \partial_{x_i} \Glap f_i$ be a
solution of the Stokes equations induced by a Stokeslet.
Then the corresponding stress tensor is given by
$\sigma_{ik} = T_{ijk} f_j$.

@@

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  + \partial_\nu \left ( -\Delta \Gbh \II
  + \nabla \otimes \nabla \Gbh \right)
  + \nabla \otimes \left ( -\Delta \Gbh \bnu
  + \partial_{\nu} \nabla \Gbh \right) \; . \nonumber
\end{equation}
Let $\btau = \bnu^\bot$. Then

\begin{equation}
  \TT_{\cdot,\cdot,k} \nu_k = -\bnu \otimes \nabla \Glap
  - \nabla^\bot \otimes \nabla^\bot \partial_\nu \Gbh
  +\nabla \otimes \nabla^\bot \partial_\tau \Gbh \; .
  \nonumber
\end{equation}

\subsubsection{Layer potentials}

We now use the Stokeslet and stresslet definitions
of the previous section to define the standard single
and double layer potentials of the Stokes eigenvalue
problem. For $\xx \in \R^2$, the single layer potential
is defined to be

\begin{equation} \label{eq:singlelayer}
  \bS [\bmu] (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy) \; .
\end{equation}
We use the notation $\bsigma_\bS[\bmu]$ to denote the
stress tensor of the single layer at any given point
$\xx \in \R^2 \setminus \Gamma$.

For $\xx \in \R^2 \setminus \Gamma$, the double layer
potential is defined to be

\begin{equation} \label{eq:doublelayer}
  \bD [\bmu] (\xx) = \int_\Gamma \left ( \TT_{\cdot,\cdot,k}(\xx,\yy)
  \nu_k(\yy)\right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where $\bnu$ denotes the outward unit normal to the boundary.
Note that when $\xx \in \Gamma$ we obtain the same formula
for the double layer potential except that the integral should be
interpreted in the principal value sense. 
If we write $\bmu = \bnu \mu_\nu + \btau \mu_\tau$,
where $\btau = \bmu^\bot$ is the positively oriented unit
tangent to the curve, then we have

\begin{align} \label{eq:stokesdlkernel}
  \left ( \TT_{\cdot,\cdot,k}(\xx,\yy)\nu_k(\yy) \right )^\intercal
  \bmu(\yy) &= \left ( - \nabla \Glap(\xx,\yy) + 2 \nabla^\bot
  \partial_{\nu\tau} \Gbh(\xx,\yy) \right ) \mu_\nu(\yy) \nonumber \\
  & \qquad+
  \nabla^\bot \left (\partial_{\tau\tau}-\partial_{\nu\nu} \right )
  \Gbh(\xx,\yy) \mu_\tau(\yy) \; .
\end{align}

When we view the layer potentials as
operators which map densities on the boundary to functions
on the boundary, we use special notation. Let

\begin{equation}
  \cS [\bmu] (\xx) = \int_\Gamma \GG (\xx,\yy) \bmu(\yy)
  \, dS(\yy)
\end{equation}
and
\begin{equation}
  \cD [\bmu] (\xx) = \oint_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\yy)
  \right )^\intercal \bmu(\yy) \, dS(\yy) \; ,
\end{equation}
where the $\oint$ symbol means that the integral is to be
evaluated in the principal value sense. For two vector valued
functions $\ff$ and $\bg$ defined on $\Gamma$, consider the bilinear
form

\begin{equation}
  \langle \ff , \bg \rangle = \int_\Gamma \ff \cdot \bg dS \; .
\end{equation}
The adjoint of $\cD$ with respect to this bilinear form
is of particular interest; we have $\cD^\intercal = \cN$, where

\begin{equation}
  \cN [\bmu] = \oint_\Gamma \left ( \TT_{\cdot,\cdot,k}\nu_k(\xx)
  \right ) \bmu(\yy) \, dS(\yy) \; .
\end{equation}

\subsubsection{Jump conditions for the layer potentials}

In formulating an integral equation, it is important
to understand the behavior of the layer potentials
defined in the previous section for points near and on the
boundary. The so-called jump conditions for the layer
potentials are summarized in the following theorem.

\begin{lemma}[Jump conditions]
  \label{lemma:jump-conds}
  Let $\bS$, $\bsigma_\bS$, $\bD$, $\cD$, and $\cN$ be
  the layer potentials and operators defined above and
  let $\Gamma$ be a sufficiently smooth domain boundary
  with outward pointing normal $\bnu$. Then, for
  a given density $\bmu$ defined on $\Gamma$,
  we have that $\bS \bmu$
  is continuous across $\Gamma$, the exterior and interior
  limits of the surface traction of $\bD \bmu$ are equal,
  and for each $\xx_0 \in \Gamma$,

  \begin{align}
    \lim_{h \downarrow 0} \bsigma_\bS[\bmu](\xx_0 \pm h\bnu(\xx_0)) \cdot \bnu(\xx_0)
    &= \mp \frac{1}{2} \bmu(\xx_0) + \cN[\bmu](\xx_0) \\
    \lim_{h \downarrow 0} \bD[\bmu](\xx_0 \pm h\bnu(\xx_0)) 
    &= \pm \frac{1}{2} \bmu(\xx_0) + \cD[\bmu](\xx_0)    \; .
  \end{align}
\end{lemma}

The above expressions are derived by noting that the
leading order singularity of these integral kernels
is the same as for the original Stokes case, so that
the standard jump conditions for Stokes
\cite{KimSangtae1991M:pa,Pozrikidis1992}
apply.
